WASP-4 is accelerating towards the Earth

### 2020-01-20 paper/ms.tex
update paper

>>>>

\subsection{Zorro imaging}

Convinced that the linear trend warranted closer examination, we
performed speckle imaging using Zorro at Gemini to attempt to detect
any nearby companions.  To our knowledge, this is the first high
resolution imaging that has been performed for WASP-4 (FIXME: IS THIS
TRUE?).

We observed WASP-4 twice with Gemini-South, 11/12 Sept. (8 sets of
1000 frames each) and 28/29 Sept. (7 sets of 1000 frames each). The
second set had better seeing and produced a slightly better result.
The spatial scale is from the diffraction limit of Gemini at the
wavelength observed to about 1.25'' plus a bit more.

% TODO: might Howell suggest a paragraph for how the contrast ratios
% were derived?
To derive contrast ratios from these images, we did XXXXX.

We would like to convert the contrast ratios obtained through the
Zorro imaging to constraints on the masses of putative companions, and
their separations from the host star.

To do this, we followed the methodology of CITE Montet+2014, and opted
to employ the CITE Baraffe+2003 models for substellar mass objects and
the MESA isochrones for stellar mass objects (CITE Choi et al XXXX).
In the intermediate regime, near 100 Mjup, we interpolated between the
two sets of models.

We assumed that companions would have contracted, and asserted the
system age to be 5 Gyr.

Due to the narrow-band filters of the Zorro imager, we further assumed
that all sources had blackbody spectra. While this is clearly false,
we do not readily have access to the planetary and stellar atmosphere
models needed for the correct calculation. However, the CITE
Baraffe+2003 and MESA models do report effective temperatures and
bolometric luminosities.  We opt to use these theoretical quantities,
combined with the measured Zorro filter wheels, to the absolute
magnitudes in the 562 and 832 nm Zorro bandpasses.  The apparent
magnitudes follow from information about the distance of the star.

Applying the same assumption to WASP-4 itself, we compute its apparent
magnitude in each of the Zorro filters, and finally derive the
transformation from contrast to companion mass.
